\textsf{Are frontier models superhuman chemists?}

### 2024-03-14 src/tex/appendix.tex
feat: add initial discussion about related work
co-authored-by: Adrian Mirza <adrianmirza81@gmail.com>

>>>>

\subsection{Related work}
Existing benchmarks such as those from \citet{guo2023large}, \cite{sun2023scieval}, \citet{Schulze_Balhorn_2024}, \citet{Cai_2024} fail to comply with most of the requirements stipulated above (see \Cref{tab:existing benchmarks}). 
While these benchmarks could provide useful insights in the short-term, they cannot follow the rapid additions to the \gls{llm} space. 
ChemBench aims to correct this through a set of developments: compatibility with BigBench, end-to-end automation, special focus on chemical safety, employment of diverse prompting strategies and specialized notation for molecules and mathematical symbols. 
Moreover, we believe that our robust framework will engage the community in open-source contributions.
